Global patterns of forest autotrophic carbon fluxes

### 2020-05-18 manuscript/manuscript draft.Rmd
added MEA ref
http://www.millenniumassessment.org/documents/document.354.aspx.pdf

Carbon cycling in forests worldwide provides the energetic basis for sustaining the majority of Earth's terrestrial biodiversity and many human populations (**REF**), while strongly influencing atmospheric CO~2~ and climate [@bonan_forests_2008]. Forests' autotrophic carbon fluxes (FACF)--that is, carbon fixation, allocation, and metabolism by trees and other primary producers--sets the energy ultimately available to heterotrophic organisms (including microbes), in turn influencing their abundance (e.g., [Zak et al. 1994](http://esajournals.onlinelibrary.wiley.com/doi/abs/10.2307/1940888); [Niedziałkowska et al. 2010](https://doi.org/10.2980/17-1-3310)) and possibly diversity [@waide_relationship_1999; Chu et al. 2019 (DOI: 10.1111/ele.13175)]. FACF influences all organic matter stocks in forest ecosystems and is linked to cycling of energy, water, and nutrients.

>>>>

Carbon cycling in forests worldwide provides the energetic basis for sustaining the majority of Earth's terrestrial biodiversity and many human populations ([MEA 2005](http://www.millenniumassessment.org/documents/document.354.aspx.pdf); **REFS**), while strongly influencing atmospheric CO~2~ and climate [@bonan_forests_2008]. Forests' autotrophic carbon fluxes (FACF)--that is, carbon fixation, allocation, and metabolism by trees and other primary producers--sets the energy ultimately available to heterotrophic organisms (including microbes), in turn influencing their abundance (e.g., [Zak et al. 1994](http://esajournals.onlinelibrary.wiley.com/doi/abs/10.2307/1940888); [Niedziałkowska et al. 2010](https://doi.org/10.2980/17-1-3310)) and possibly diversity [@waide_relationship_1999; Chu et al. 2019 (DOI: 10.1111/ele.13175)]. FACF influences all organic matter stocks in forest ecosystems and is linked to cycling of energy, water, and nutrients.
